### 2019-04-15 report/chapter01.Rnw
Update

In science, there is not only a need for accumulation of knowledge, but also for concentration. For the same reason as statistical analysis is performed on single experiments, it can also be used for results of multiple experiments or studies: to simplify and summarize the data at hand to a degree that is understandable. The latter procedure goes usually under the name of meta-analysis. Meta analyses are used to summarize results and evidence over multiple studies when they are considered to be similar enough.

\vspace{0mm}
In the face of the large amount of research that is done in some fields of empirical science, meta-analysis becomes increasingly important, for looking at all evidence would simply take very long for one person. Meta-analyses are often part of a systematic review, an effort of experts of a field to provide an overlook over the evidence. In the course of a review, all literature and data with respect to a scientific question is collected and a meta-analysis is operated at the end to summarize the findings.

\vspace{0mm}
In the case of clinical science, systematic reviews and meta-analyses do not only benefit scientists but also patients and clinicians, for both are provided with up-to-date summaries of current evidence with respect to a certain treatment. Therefore, meta-analysis is at the core of what is called evidence-based medicine.

\vspace{0mm}
However, there are problems that potentially limit the validity of meta-analysis; studies at hand can be biased or heterogeneity between study results can be large and the number of studies small. The importance and the issues of meta-analysis are the reasons why they have been chosen as one general topic of the masters thesis. One particular problem will furthermore be investigated in more detail: reporting bias and meta-analysis. Not only will the methods to deal with issues as reporting bias be discussed, but also will they be applied on a dataset of systematic reviews that can be used for meta-analysis. So at the end of the report, the reader will not only have an impression of the technical issues caused by reporting bias, but also of the abundance and extent of it in the dataset. Since the dataset is very large and of good quality, results might also be representative to some extent for reporting bias in clinical science.

>>>>

Meta-analysis is at the core of evidence based medicine because it allows to summarise evidence over multiple studies and provide a more broad view on success and effectivity of clinical treatments. The necessity of meta-analyses is also increased by the abundance of data and publications. Especially when the findings differ or even contradict between studies, meta-analysis is the only way to go if one wants to make decisions based on quantitative and scientific criteria.

\vspace{0mm}
For this, meta-analyses do not only benefit research, but also clinical practice, and may lead to better health care and prevention. However, the usefulness of meta-analysis does not restrict to clinical science, but to any empirical and quantiative science.

\vspace{0mm}
Usually, a meta-analysis is part of a systematic review where researchers decided to summarise all research in a given field or more specifically, that concerns a given question. Meta-analysis can be applied to all studies that are approximately identical in their experimental setup and the way the outcome of the experiments is measured. In systematic reviews where meta-analyses are used, the conclusions are most often strongly based on the results and the interpretation of the meta-analysis.

\vspace{0mm}
However, there are problems that potentially limit the validity of meta-analysis; the number of studies available can be incomplete or the results of the studies can be biased. Some of those problems can be solved or asserted by special statistical methods.

\subsection{Small Study Effects or Publication Bias}
When study sample size decreases, the probability of extreme and missleading results in a study increases. This becomes a problem if results are selectively published, and therefore available, based on their results. When this is the case, one speaks of a small study effect or of ``Publication bias''.

\vspace{0mm}
The issue has been discussed extensively in the last years, most often in the context of what has came to be known as the replication crisis. The reasons for small study effects are manifold, but originate most often in the myopical acting of agents in science and the lack of statistical education. Studies are reported by scientists, published by journals and noticed by readers more often if their findigs are positive and find e.g. a substantive difference or effect. When doing a meta-analysis, one again obtains biased results.

\vspace{0mm}
The reason why that is less of an issue for larger studies is that extreme results are in general less likely and that due to larger effort, a result is published although there has been no clear and positive findings.

\vspace{0mm}
While there is generally no way to assert poor study quality, small study effect can in principle be asserted and corrected for statistically. This masters thesis will mainly be about statistical methods to detect and adjust for small study effects. It can furthermore be divided in two parts:
\begin{itemize}
\item Methodological part: Collection and discussion of statistical tests and correction methods for small study effects.
\item Applied part: Application of the methods to studies of the Cochrane Library of systematic Reviews. Subsequent discussion of the implications
of the results for clinical science.
\end{itemize}

In contrast to simulation studies, it is not possible to assess critical properties of the methods such as the power of a test, since the truth is not known. But based on the amount of data, one can of course try to make extrapolation to tendencies in clinical science in general. Moreover, it is still interesting to see how the methods behave in general, especially with respect to each other. It may, as an example, be possible to answer the question which statistical test is most conservative and which pooling method is most optimistic on average. Comparison with results from simulations may allow to speculate about the reasons when simulation and real world results diverge.

### 2019-04-15 report/chapter03.Rnw
Update

load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))

@@

\vspace{0mm}
There are tests that can be applied to find out if reporting bias is present in the meta analysis. For the precise description, see the methods section. Application of the tests is only recommended if there are ten or more studies that can be used, so all meta-analyses with less than ten studies have been excluded.

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore, the results of the tests are separated in continuous outcome test results and dichotomoized outcome results. In Figure \ref{bias.results.bin} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for dichotomous outcomes. The same is shown in Figure \ref{bias.results.cont} for continuous outcome measures.

% # <<results = 'asis', Echo = FALSE>>=
% # rejection.bin <- data.bin.ext %>% summarize(egger.rejection = mean(egger.test),
% #                                             schwarzer.rejection = mean(schwarzer.test),
% #                                             rucker.rejection = mean(rucker.test),
% #                                             harbord.rejection = mean(harbord.test),
% #                                             peter.rejection = mean(peter.test))
% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
% # @

\begin{figure}
<<echo=FALSE>>=
bin.spread <- data.bin.ext %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type)
bin.spread$value <- ifelse(bin.spread$value == 1, "rejected", "accepted")
bin.spread$value <- factor(bin.spread$value)
bin.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cont.spread <- data.cont.ext %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type)
cont.spread$value <- ifelse(cont.spread$value == 1, "rejected", "accepted")
cont.spread$value <- factor(cont.spread$value)
cont.spread %>% ggplot(aes(x = test.type, fill = value)) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

Furthermore, one can investigate how well the tests give the same results, i.e. classify the same study collections as having publication bias. This is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types.

<<results = 'asis', echo = FALSE>>=
data.bin.ext <- data.bin.ext %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))

agreement.bin <- data.bin.ext %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                        egger.peter = sum(egger.peter == "agree")/n(),
                                        egger.rucker = sum(egger.rucker == "agree")/n(),
                                        egger.harbord = sum(egger.harbord == "agree")/n(),
                                        schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
                                        schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
                                        schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
                                        rucker.peter = sum(rucker.peter == "agree")/n(),
                                        harbord.peter = sum(harbord.peter == "agree")/n())

correlation.bin <- data.bin.ext %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                            egger.peter = cor(pval.egger.bin, pval.peter.bin),
                                            egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
                                            egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
                                            schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
                                            schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
                                            schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
                                            rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
                                            harbord.peter = cor(pval.harbord.bin, pval.peter.bin))

@@

print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@

<<results = 'asis', echo = FALSE>>=
data.cont.ext <- data.cont.ext %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))

agreement.cont <- data.cont.ext %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                              thomson.begg = sum(thomson.begg == "agree")/n(),
                                              egger.begg = sum(egger.begg == "agree")/n())

correlation.cont <- data.cont.ext %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))

@@

print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes. %(Suggests that 10 is likely too small)

\begin{figure}
<<echo=FALSE>>=
data.bin.ext %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
\label{pvalues.samplesize.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
data.cont.ext %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
\label{pvalues.samplesize.cont}
\end{figure}

<<echo=FALSE>>=
trimfill.cont <- data %>% filter(outcome.measure == "Mean Difference" | outcome.measure == "Std. Mean Difference") %>% #filter(file.nr < 50) %>% 
  filter(sd1 > 0 & sd2 > 0 ) %>% filter(!is.na(sd1) & !is.na(sd2)) %>% 
  filter(mean1 != 0 | mean2 != 0 ) %>% filter(!is.na(mean1) & !is.na(mean2)) %>% 
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metacont(n.e = total1, mean.e = mean1, sd.e = sd1, n.c = total2, mean.c = mean2, sd.c = sd2))$k0 / n())

trimfill.cont.mean <- trimfill.cont %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
trimfill.cont.median <- trimfill.cont %>% ungroup %>% summarise(median = median(trim)) %>% select(median)

trimfill.bin <- data %>% filter(outcome.measure == "Risk Ratio" | outcome.measure == "Odds Ratio") %>% #filter(file.nr < 503) %>% 
  filter(events1 > 0 | events2 > 0) %>% 
  filter(total1 - events1 > 0 | total2 - events2 > 0) %>%
  group_by(file.nr, outcome.nr, subgroup.nr) %>% 
  mutate(n = n()) %>% filter(n > 9) %>% 
  summarize(trim = trimfill(metabin(event.e = events1, n.e = total1, event.c = events2, n.c = total2))$k0 / n())

trimfill.bin.mean <- trimfill.bin %>% ungroup %>% summarise(mean = mean(trim)) %>% select(mean)
trimfill.bin.median <- trimfill.bin %>% ungroup %>% summarise(median = median(trim)) %>% select(median)
@

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}. In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes.

\begin{figure}
<<echo=FALSE>>=
trimfill.cont %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

@@

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
trimfill.bin %>% ggplot(aes(x = trim)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = data.bin.ext$trim.bin, y = as.factor(ifelse(data.bin.ext$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of peters test and dichotomous outcomes}
\label{trimfill.pvalues.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = data.cont.ext$trim.cont, y = as.factor(ifelse(data.cont.ext$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of thomson and sharp's test and continuous outcomes}
\label{trimfill.pvalues.cont}
\end{figure}

>>>>

load(file.path(PATH_RESULTS, 'PubBias_results1.RData'))
load(file.path(PATH_RESULTS, 'PubBias_results2.RData'))
load(file.path(PATH_RESULTS, 'PubBias_results3.RData'))
load(file.path(PATH_RESULTS, 'PubBias_results4.RData'))

@@

\subsection{Small Study Effect Tests}

<<echo=FALSE, warning=FALSE>>=
n.bin <- dim(meta.bin)[1]
rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
                                            schwarzer.rejection = mean(schwarzer.test),
                                            rucker.rejection = mean(rucker.test),
                                            harbord.rejection = mean(harbord.test),
                                            peter.rejection = mean(peter.test))

bin.spread <- meta.bin %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type, value = "null.hypothesis")
bin.spread$null.hypothesis <- ifelse(bin.spread$null.hypothesis == 1, "rejected", "not rejected")
bin.spread$null.hypothesis <- factor(bin.spread$null.hypothesis)

meta.bin <- meta.bin %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))

agreement.bin <- meta.bin %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                        egger.peter = sum(egger.peter == "agree")/n(),
                                        egger.rucker = sum(egger.rucker == "agree")/n(),
                                        egger.harbord = sum(egger.harbord == "agree")/n(),
                                        schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
                                        schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
                                        schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
                                        rucker.peter = sum(rucker.peter == "agree")/n(),
                                        harbord.peter = sum(harbord.peter == "agree")/n())

correlation.bin <- meta.bin %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                            egger.peter = cor(pval.egger.bin, pval.peter.bin),
                                            egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
                                            egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
                                            schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
                                            schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
                                            schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
                                            rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
                                            harbord.peter = cor(pval.harbord.bin, pval.peter.bin))

@@

#Continuous outcomes:
n.cont <- dim(meta.cont)[1]
rejection.cont <- meta.cont %>% summarize(egger.rejection = mean(egger.test),
                                              begg.rejection = mean(begg.test),
                                              thomson.rejection = mean(thomson.test))

cont.spread <- meta.cont %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type, value = "null.hypothesis")
cont.spread$null.hypothesis <- ifelse(cont.spread$null.hypothesis == 1, "rejected", "not rejected")
cont.spread$null.hypothesis <- factor(cont.spread$null.hypothesis)

meta.cont <- meta.cont %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))

agreement.cont <- meta.cont %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                              thomson.begg = sum(thomson.begg == "agree")/n(),
                                              egger.begg = sum(egger.begg == "agree")/n())

correlation.cont <- meta.cont %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))

@@

#Trimfill missing studies fractions statistics:
trimfill.cont.mean <- meta.cont %>% ungroup %>% summarise(mean = mean(missing.trim.cont)) %>% select(mean)
trimfill.cont.median <- meta.cont %>% ungroup %>% summarise(median = median(missing.trim.cont)) %>% select(median)

trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
@

There are tests that can be applied to find out if reporting bias is present in the meta analysis. For the precise description, see the methods section. Application of the tests is only recommended if there are ten or more studies \citep{cochrane.handbook} that can be used, so all meta-analyses with less than ten studies have been excluded.

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes. From \Sexpr{n.cont} meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (\Sexpr{round(rejection.cont$thomson.rejection, 3)}), followed closely by Eggers test (\Sexpr{round(rejection.cont$egger.rejection, 3)}) and Begg and Mazumdar's test (\Sexpr{round(rejection.cont$begg.rejection, 3)}).
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}). The test that rejects most null hypotheses is here Egger's test (\Sexpr{round(rejection.bin$egger.rejection, 3)}), followed by R\"ucker's test (\Sexpr{round(rejection.bin$rucker.rejection, 3)}), Harbord's test (\Sexpr{round(rejection.bin$harbord.rejection, 3)}), Peters test (\Sexpr{round(rejection.bin$peter.rejection, 3)}) and Schwarzer's test (\Sexpr{round(rejection.bin$schwarzer.rejection, 3)}).

\begin{figure}
<<echo=FALSE>>=
cont.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis )) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=

bin.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

The agreement of the tests, i.e. the proportion of meta-analyses where the rest results are equal between tests, is shown in Table \ref{agreement.bin} and Table \ref{agreement.cont}, again separated for outcome types. Agreement in tests for binary outcomes is better than continuous outcomes, with some variation between tests (binary outcomes: 83 to 91\%). Correlation varies more between tests, both for continuous and binary outcome tests.

<<results = 'asis', echo = FALSE, warnings = FALSE>>=
print(xtable(x = t(binary.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (dichotomous outcomes)", label = "agreement.bin",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@

<<results = 'asis', echo = FALSE, warnings = FALSE>>=
print(xtable(x = t(cont.tests.agreement), caption = "Proportion of tests that agree in rejection ar acceptance of the null hypothesis that there is no small study effect (continuous outcomes)", label = "agreement.cont",  align = "lll", digits = 2), include.rownames = T, size = "footnotesize")
@

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes. %(Suggests that 10 is likely too small)
A trend towards more significant p-values is visible for larger sample sizes.

\begin{figure}
<<echo=FALSE>>=
meta.bin %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
\label{pvalues.samplesize.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
meta.cont %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
\label{pvalues.samplesize.cont}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}. A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

\begin{figure}
<<echo=FALSE>>=
meta.cont %>% ggplot(aes(x = missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

@@

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = meta.bin$missing.trim.bin, y = as.factor(ifelse(meta.bin$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
\label{trimfill.pvalues.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = meta.cont$missing.trim.cont, y = as.factor(ifelse(meta.cont$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
\label{trimfill.pvalues.cont}
\end{figure}

\subsection{Small Study Effect Correction}

Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.

% # <<results = 'asis', Echo = FALSE>>=
% # rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
% #                                             schwarzer.rejection = mean(schwarzer.test),
% #                                             rucker.rejection = mean(rucker.test),
% #                                             harbord.rejection = mean(harbord.test),
% #                                             peter.rejection = mean(peter.test))
% # print(xtable(rejection.bin), label = "bias.results", caption = "Cumulative number of groups with number of reproduction trials >= n", align = "llll", digits = 0), include.rownames = F, size = "footnotesize")
% # @
